A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

Perhaps, the works of \citet{Afra_2013}, \citet{Afra_2016}, \citet{Afra_2014}, \citet{Insuasty_2017} are more closely related to the one performed here. However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization. The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same CVFEM simulator used in this work. However, like the work of \citet{Tavakoli_2010}, the \citeauthor{Xiao_2018} were more interested in reducing the number of variable used to describe the system.

>>>>

Perhaps, work performed by \citet{Afra_2013,Afra_2016,Afra_2014} and \citet{Insuasty_2017} are more closely related to the one performed here. However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization. The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same flow simulator model used in this work. However, similarly to \citet{Tavakoli_2010}, \citeauthor{Xiao_2018} focused on reducing the number of variable used to describe the system.
